Efficient Community Formation \\ for Web Services

### 2014-01-03 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

\textbf{Web Service Community.}
Community of web services is a collection of web services with same functionallity having a 
coordinator and communication end point, which is the access point to the community. In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon recieving a request on run-time. They have proposed a scoring service based on non-functional requrement of the task and web service capabilties to dynamicly chose the web service to perform the task upon reciving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service coimmunities as a collection of web services with a common functionality but different QoS properties. A community manager upon recieving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requres aggregation of different type of services to satisfy a request.

>>>>

\textbf{Web Service Community.}
Communities of web services are a collection of web services with same functionallity having a 
coordinator or service broker as manager and also the access point to the community. In \cite{DBLP:journals/internet/BenatallahSD03}, Behatallah et al. defined communities as \emph{Service Containers} which aggregates substitutable web services providing a common functionality (same set of operations). They abstracted \emph{Service Containers} as web services which are created, advertised, discovered and invoked just as elementary web services, they \emph{Container} as a manager is responsible for the mentioned tasks and also web service selection upon recieving a request on run-time. They have proposed a scoring service based on non-functional requrement of the task and web service capabilties to dynamicly chose the web service to perform the task upon reciving requests. A similar concept was proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}. They introduced web service coimmunities as a collection of web services with a common functionality but different QoS properties. A community manager upon recieving a request, delegates the request to one of its current members. The choice is based on history and quality metrics of each web service. They have proposed an efficient global web service selection algorithm in order to approach quality constraints and preferences for composite services which requres aggregation of different type of services to satisfy a request.
